Analysing Constraint Grammar with a SAT solver

### 2015-10-09 paper/lrec/problem_desc.tex
stuff^2

\section{Introduction}

@@

The technique requires an existing morphological lexicon, but no corpus.

>>>>

\section{Introduction}
\label{sec:intro}

@@

The technique requires an existing morphological lexicon, but no corpus.
This makes it suitable also for languages without large corpora.
Authors writing grammars for well-resourced languages can also benefit from the technique, as an additional tool along with a gold standard corpus. 
Hand-annotated corpora are commonly used in the development of CGs
 \cite{voutilainen99}, because they give immediate feedback whether a new rule
increases or decreases accuracy, and by how large margin.

\todo{Relate to conf themes: "Methodologies and tools for LRs construction and annotation" and
"Validation and quality assurance of LRs"}

% * Describe problem: CGs are huge & prone to mistakes,
%  * we are looking at conflicts such as ...
%  * if you forgot a case
%  * some evidence that big CGs have conflicts and this is a real problem
%  * Eckhard's paper to explain why conflicting rules are a problem
%  * Goal: help grammar writer while they are writing the grammar, to avoid these kinds of problems
%  * Examples

% * Describe the technique

% * Preliminary results
%  - dutch & spanish
%  - mention scalability
%  - talk about size of SAT problem -- give number of SAT clauses for the last rule in the biggest grammar I have

% * Future work
%  - analysing different grammar formalisms
%  - asking different questions
%  - restrict yourself to readings that are actually words
